### 2020-04-28 Paper/paper.tex
added abstract and key terms to paper

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

@@

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

>>>>

\begin{abstract}
Information that best describes galaxy mergers is sparse.  Complications arise when forming postulations due to missing information such as orbital mass-ratios, orbital velocities, and orientations.  To remedy this, we devised two neural networks to analyze images and human scores from Galaxy Zoo: Mergers in the hopes that a well-fitting model - one that can find true dynamic parameters for galaxy collisions.  In the single layer neural network, the information is parsed to inform the convolution net about hyperparameters such as batch or epoch sizes.  The convolution model is designed to assign a fitness score to an input galaxy image.  That score represents an approximation of how well the image fits into predicted galaxy collision simulations.  Through the limited scope of this project there are points of interest.  Both networks achieved successful validation while eventually overfitting.  The convolution net managed with good accuracy to predict scores of mergers when compared to human grading and, perhaps, more accurate than the human scores. Though the data set we used is small and unevenly distributed, there are hopeful interpretations of the results.  Better and more data sets along with more network layers may yield better results in the future.  With more tuning, our neural networks may eliminate the need for further human rankings
\end{abstract}

@@

\begin{IEEEkeywords}
convolutional neural networks, single layer neural networks, CNN, regression model, galaxy collisions, image scoring
\end{IEEEkeywords}
